Supplementary Information

### 2020-08-11 docs/supplementary_information.Rmd
put ms into docs and just keep necessary files
keep also tex in appendix

---
output:
  bookdown::pdf_document2:
    keep_tex: no
    latex_engine: xelatex
    # float is needed for floating figures
    extra_dependencies: ["fontspec", "sectsty", "float"]
    toc: false
    fig_caption: yes
    number_sections: true
header-includes:
  # adjust figure captions
  - \usepackage{caption}
  - \captionsetup{font={footnotesize,bf,singlespacing}}
  # Ecography requires double line spacing and line numbering
  - \usepackage{setspace}
  - \doublespacing
  - \usepackage{lineno}
  - \linenumbers
  # Use Appendix instead of Figure in the caption
  - \renewcommand{\figurename}{Appendix}

title: Supplementary Information
bibliography: ../transect_refs.bib
csl: ../ecography.csl
# biblio-style: "natbib"
link-citations: true
---

>>>>

---
output:
  bookdown::pdf_document2:
    keep_tex: yes
    latex_engine: xelatex
    # float is needed for floating figures
    extra_dependencies: ["fontspec", "sectsty", "float"]
    toc: false
    fig_caption: yes
    number_sections: true
header-includes:
  # adjust figure captions
  - \usepackage{caption}
  - \captionsetup{font={footnotesize,bf,singlespacing}}
  # Ecography requires double line spacing and line numbering
  - \usepackage{setspace}
  - \doublespacing
  - \usepackage{lineno}
  - \linenumbers
  # Use Appendix instead of Figure in the caption
  - \renewcommand{\figurename}{Appendix}

title: Supplementary Information
bibliography: transect_refs.bib
csl: ecography.csl
# biblio-style: "natbib"
link-citations: true
---
